The development of infants' responses to mispronunciations: A Meta-Analysis

### 2020-02-07 VonHolzenBergmann_MPMetaAnalysis.tex
Dev Psych submission

\linenumbers
\usepackage{setspace}
\usepackage{fontspec}
\newfontfamily\ipa{Doulos SIL}
\DeclareTextFontCommand{\ipatext}{\ipa}
\AtBeginEnvironment{tabular}{\singlespacing}
\AtBeginEnvironment{lltable}{\singlespacing}
\AtBeginEnvironment{tablenotes}{\doublespacing}
\captionsetup[table]{font={stretch=1.5}}
\captionsetup[figure]{font={stretch=1.5}}

@@

\abstract{
As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words. To do so, they must strike a balance between accepting speaker dependent variation (e.g.~mood, voice, accent), but appropriately rejecting variation when it (potentially) changes a word's meaning (e.g.~cat vs.~hat). This meta-analysis focuses on studies investigating infants' ability to detect mispronunciations in familiar words, or mispronunciation sensitivity. Our goal was to evaluate the development of mispronunciation sensitivity in infancy as well as explore the role of experimental manipulations related to theoretical questions and analysis choices. The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects. Interestingly, this ability is not modulated by age or vocabulary size, suggesting that a mature understanding of native language phonology may be present in infants from an early age, possibly before the vocabulary explosion. The results also support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation modulate mispronunciation sensitivity. We also shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity. Our paper concludes with recommendations for improved practice in testing infants' word and sentence processing on-line.

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts that differentiate words in a given language (e.g.~cat-hat). Twenty years' worth of studies have examined infants' application of phonological category knowledge during word recognition through the mispronunciation sensitivity paradigm to probe the development of this latter distinction. At this point, a picture on the functional use of language-specific phonetic and phonological knowledge began to emerge. At the turn of the millennium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream (Jusczyk \& Aslin, 1995) and learning minimal pairs (Stager \& Werker, 1997). Both studies and the lines of research they sparked showed that under the right conditions, even young infants can use their emerging native language phonological skills during word-level language processing.

Swingley and Aslin (2000) expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition. American-English learning 18- to 23-month-olds were presented with pairs of images of words they were very likely to know (e.g.~a baby and a dog) and their eye movements to each image were recorded. Infants either heard the correct label (e.g.~\enquote{baby}) or a mispronounced label (e.g.~\enquote{vaby}) for one of the images. Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looks to the target image than mispronounced labels. Swingley and Aslin (2000) concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.

Why should sensitivity to mispronunciations pose a challenge to the young infant and thus the findings of Swingley and Aslin (2000) be found novel? There are two key challenges the infant learner has to contend with. First, the native language being learned determines the relevant contrasts for the infant language-learner. These contrasts are therefore not innate, but must be learned. For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish. Second, across talkers, these sounds might be realized differently, and change even as the talker talks to an infant or adult (e.g.~Benders, 2013). As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired and applied to lexical representations. The time is thus ripe to aggregate all publicly available evidence using a meta-analysis. In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see Frank, Braginsky, Yurovsky, and Marchman (2017); ManyBabiesConsortium (2020); for notable exceptions). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

@@

An \emph{increase} in mispronunciation sensitivity is predicted by a maturation in phono-lexical representations from holistic to more detailed and has been supported by several studies (Altvater-Mackensen, 2010; Altvater-Mackensen, Feest, \& Fikkert, 2014; Feest \& Fikkert, 2015; Mani \& Plunkett, 2007). More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop. The first words that infants learn are often not similar sounding (e.g.~mama, ball, kitty; Charles-Luce \& Luce, 1995) and encoding representations for these words using fine phonological detail may not be necessary. \textbf{According to PRIMIR (Curtin, Byers-Heinlein, \& Werker, 2011; Curtin \& Werker, 2007; Werker \& Curtin, 2005) infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.} A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations (Barton, Miller, \& Macken, 1980). This argument is supported by the results of Mani and Plunkett (2010). Here, 12-month-old infants were divided into low and high vocabulary groups. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations (see below for further discussion on consonant-vowel assymmetry). If increasing age and/or vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship of either with mispronunciation sensitivity.

@@

There are no theoretical accounts that would predict \emph{decreased} mispronunciation sensitivity, but at least one study has found a decrease in sensitivity to small mispronunciations . Mani and Plunkett (2011) tested 18- and 24-month-olds' sensitivity to increasingly larger mispronunciations: 1- (bed-bud), 2- (foot-fit), and 3-feature phonological changes (doll-deal). Although both age groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to more subtle 1-feature mispronunciations. To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below). In contrast, 18-month-olds did not show graded sensitivity, showing similar disruptions to word recognition for smaller and larger mispronunciations.

To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size. But, this may not account for all variability found in the literature. Although infant mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the location of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image. These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. We thus follow our analyses of a developmental trajectory with one of features of the task, and line out here task effects which can shed further light on early phono-lexical representations and their maturation.

@@

Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults (Nazzi \& Cutler, 2018) and infants (Nazzi, Poltrock, \& Von Holzen, 2016), known as the consonant bias. A learned account predicts that a consonant bias emerges over development (Floccia, Nazzi, Luche, Poltrock, \& Goslin, 2014; Keidel, Jenison, Kluender, \& Seidenberg, 2007; Nazzi et al., 2016) and that this emergence is impacted by the language family of the infants' native language (Nazzi et al., 2016). In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- (Mani \& Plunkett, 2007, 2010) and Danish-learning infants (Højen et al., n.d.) and do not compare infants learning different native languages (for evidence from word-learning see Floccia et al., 2014; Nazzi, Floccia, Moquet, \& Butler, 2009). One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016). In the current meta-analysis, we examine infants' sensitivity to the \emph{type of mispronunciation}, whether consonant or vowel, across different ages and native language families to assess the predictions of the learned account of the consonant bias.

@@

@@

\hypertarget{insert-figure-reffigprisma-image-about-here}{%
\subsection{(Insert Figure \ref{fig:PRISMA-image} about here)}\label{insert-figure-reffigprisma-image-about-here}}

\begin{figure}
\includegraphics[width=1.6in]{figures/Figure_1_PRISMA_MA_Mispronunciation} \caption{A PRISMA flowchart illustrating the selection procedure used to include studies in the current meta-analysis.}\label{fig:PRISMA-image}
\end{figure}

@@

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the google scholar search engine to search for papers citing the original Swingley and Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (\emph{n} = 32) consisted of 27 journal articles, 1 proceedings paper, 2 theses, and 2 unpublished reports. We will refer to these items collectively as papers. Table \ref{tab:SummaryTable} provides an overview of all papers included in the present meta-analysis.

\hypertarget{insert-table-1-about-here}{%
\subsection{(Insert Table 1 about here)}\label{insert-table-1-about-here}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Condition: Were words mispronounced or not;
\item
  Mean age reported per group of infants, in days;
\item
  Vocabulary size, measured by a standardized questionnaire or list;
\item
  Position of mispronunciation: onset, medial, offset, or mixed;
\item
  Size of mispronunciation, measured in features changed;
\item
  Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
\item
  Type of mispronunciation: consonant, vowel, or both;
\item
  Distractor familiarity: familiar or unfamiliar;
\end{enumerate}

@@

Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper. Most papers (\emph{n} = 52 records from 13 papers) subtracted the PTL score for a pre-naming baseline phase from the PTL score for a post-naming phase and report a difference score.

Other papers either compared post- and pre-naming PTL with one another (\emph{n} = 29 records from 10 papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50\% (\emph{n} = 23 records from 9 papers). For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming baseline PTL) indicate target looks towards the target object after hearing the label, i.e.~a recognition effect. Standardized effect sizes based on mean differences, as calculated here, preserve the sign. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.

@@

The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R (R Core Team, 2018) package metafor (Viechtbauer, 2010). To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model. Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the package meta (Schwarzer, 2007). For a subsequent investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, phonological overlap between target and distractor labels, type of mispronunciation, and distractor familiarity (more detail below).

@@

\hypertarget{insert-figure-reffigfunnelcombo-about-here}{%
\subsection{(Insert Figure \ref{fig:FunnelCombo} about here)}\label{insert-figure-reffigfunnelcombo-about-here}}

@@

Heterogeneity was significant for both correctly pronounced (Q(103) = 625.63, \emph{p} \textless{} .001) and mispronounced words, (Q(146) = 462.51, \emph{p} \textless{} .001), as well as mispronunciation sensitivity, which included the moderator condition (QE(249) = 1,088.14, \emph{p} \textless{} .001). This indicated that the sample contains unexplained variance leading to significant difference between studies beyond what is to be expected based on random sampling error. We therefore continue with our moderator analysis to investigate possible sources of this variance.

@@

\hypertarget{insert-figure-reffigplotmpeffect-about-here}{%
\subsection{(Insert Figure \ref{fig:PlotMPEffect} about here)}\label{insert-figure-reffigplotmpeffect-about-here}}

@@

\hypertarget{insert-figure-reffigvocabdescribe1-about-here}{%
\subsection{(Insert Figure @ref(fig:Vocabdescribe1 about here)}\label{insert-figure-reffigvocabdescribe1-about-here}}

@@

\hypertarget{insert-figure-reffigplotfeateffect-about-here}{%
\subsection{(Insert Figure \ref{fig:PlotFeatEffect} about here)}\label{insert-figure-reffigplotfeateffect-about-here}}

@@

\hypertarget{insert-figure-reffigplotmispposit-about-here}{%
\subsection{(Insert Figure \ref{fig:PlotMispPosit} about here)}\label{insert-figure-reffigplotmispposit-about-here}}

@@

We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to the type of mispronunciation, consonant or vowel. Furthermore, sensitivity to consonant and vowel mispronunciations is hypothesized to differ depending on whether the infant is learning a Germanic or Romance language. We therefore conducted two sets of analyses, one analyzing consonants and vowels alone and a second including langauge family as a moderator. We did not include data for which mispronunciation type varied within experiment and was not reported separately (\emph{n} = 23). The analysis was therefore based on a subset of the overall dataset, comparing records with consonant (\emph{n} = 145) and vowel (\emph{n} = 71) mispronunciations.

@@

\hypertarget{insert-figure-reffigplotmisptype-about-here}{%
\subsection{(Insert Figure \ref{fig:PlotMispType} about here)}\label{insert-figure-reffigplotmisptype-about-here}}

@@

\hypertarget{insert-figure-reffigplotcveffectlang-about-here}{%
\subsection{(Insert Figure \ref{fig:PlotCVEffectLang} about here)}\label{insert-figure-reffigplotcveffectlang-about-here}}

@@

When age was added as a moderator, the moderator test was significant, QM(7) = 67.82, \emph{p} \textless{} .001 and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small (\(\beta\) = = 0.091, SE = 0.038, 95\% CI{[}0.017, 0.166{]}, \emph{p} = 0.016. As can be seen in Figure \ref{fig:PlotDistOverlap}b, mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap.

@@

\hypertarget{insert-figure-reffigplotdistoverlap-about-here}{%
\subsection{(Insert Figure \ref{fig:PlotDistOverlap} about here)}\label{insert-figure-reffigplotdistoverlap-about-here}}

@@

We examine whether variation in the approach to data analysis may be have an influence on our conclusions regarding infants' developing mispronunciation sensitivity. To do so, we analyzed analysis choices related to timing (post-naming analysis window; offset time) and type of dependent variable in our coding of the dataset because they are consistently reported. Further, since we observe variation in both aspects of data analysis, summarizing typical choices and their impact might be useful for experiment design in the future and might help establish field standards. In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have on reported mispronunciation sensitivity and its development. We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as moderator.

@@

Although there are a priori reasons, such as infant age or previous studies, to choose the post-naming analysis window or offset time, these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman \& Loken, 2013). Considering that these choices were systematically different across infant ages, at least for the post-naming analysis window, we next explored whether the post-naming analysis window length or the offset time influenced our estimate of infants' sensitivity to mispronunciations.

@@

Considering that we found a significant relationship between the post-naming analysis window length and infant age, such that younger ages had a longer window of analysis, we next examined whether post-naming analysis window length modulated the estimated size of mispronunciation sensitivity as infant age changed. When age was included as a moderator, the moderator test was significant (QM(7) = 247.322, \emph{p} \textless{} .001). The estimate for the three-way-interaction between condition, post-naming analysis window, and age was small, but significant (\(\beta\) = -0.04, SE = 0.014, 95\% CI{[}-0.068, -0.012{]}, \emph{p} = 0.006). As can be seen in Figure \ref{fig:PlotPostNameCondAge}b, when records were analyzed with a post-naming analysis window of 2000 ms or less (a limit we imposed for visualization purposes), mispronunciation sensitivity seems to increase with infant age. If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation between mispronunciation sensitivity and age. In other words, all three possible developmental hypotheses might be supported depending on analysis choices made regarding post-naming analysis window length. These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming analysis window.

\hypertarget{insert-figure-reffigplotpostnamecondage-about-here}{%
\subsection{(Insert Figure \ref{fig:PlotPostNameCondAge} about here)}\label{insert-figure-reffigplotpostnamecondage-about-here}}

@@

Similar to post-naming analysis window length, all three possible developmental hypotheses might be supported depending on the dependent variable reported. In other words, choice of dependent variable may influence the conclusion drawn regarding how mispronunciation sensitivity may change with infant age. We address this issue in the General Discussion.

\hypertarget{insert-figure-reffigplotwithincondagediffscore-about-here}{%
\subsection{(Insert Figure \ref{fig:PlotWithinCondAgeDiffScore} about here)}\label{insert-figure-reffigplotwithincondagediffscore-about-here}}

>>>>

\linenumbers
\usepackage{setspace}
\usepackage{fontspec}
\usepackage{tipa}
\AtBeginEnvironment{tabular}{\singlespacing}
\AtBeginEnvironment{lltable}{\singlespacing}
\AtBeginEnvironment{tablenotes}{\doublespacing}
\captionsetup[table]{font={stretch=1.5}}
\captionsetup[figure]{font={stretch=1.5}}

@@

\abstract{
As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words. To do so, they must strike a balance between accepting speaker dependent variation (e.g.~mood, voice, accent), but appropriately rejecting variation when it (potentially) changes a word's meaning (e.g.~cat vs.~hat). This meta-analysis focuses on studies investigating infants' ability to detect mispronunciations in familiar words, or mispronunciation sensitivity. Our goal was to evaluate the development of infants' phonological representations for familiar words as well as explore the role of experimental manipulations related to theoretical questions and analysis choices. The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects. Interestingly, this ability is not modulated by age or vocabulary size, suggesting that a mature understanding of native language phonology may be present in infants from an early age, possibly before the vocabulary explosion. These results also support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation. We also shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity. Our paper concludes with recommendations for improved practice in testing infants' word and sentence processing on-line.

@@

In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts that differentiate words in a given language (e.g.~cat-hat). Twenty years' worth of studies have examined infants' application of phonological category knowledge during word recognition through the mispronunciation sensitivity paradigm to probe the development of this latter distinction. At this point, a picture on the functional use of language-specific phonetic and phonological knowledge began to emerge. At the turn of the millennium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream (Jusczyk \& Aslin, 1995) and learning minimal pairs (Stager \& Werker, 1997). Both studies and the lines of research they sparked showed that under the right conditions, even young infants can use their emerging native language phonological skills during word-level language processing.
Swingley and Aslin (2000) expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition. American-English learning 18- to 23-month-olds were presented with pairs of images of words they were very likely to know (e.g.~a baby and a dog) and their eye movements to each image were recorded. Infants either heard the correct label (e.g.~\enquote{baby}) or a mispronounced label (e.g.~\enquote{vaby}) for one of the images. Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looks to the target image than mispronounced labels. Swingley and Aslin (2000) concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.

Why should sensitivity to mispronunciations pose a challenge to the young infant and thus the findings of Swingley and Aslin (2000) be found novel? There are two key challenges the infant learner has to contend with. First, the native language being learned determines the relevant contrasts for the infant language-learner. These contrasts are therefore not innate, but must be learned. For an infant learning Catalan, the vowel contrast /e/-/\textipa{E}/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish. Second, across talkers, these sounds might be realized differently, and change even as the talker talks to an infant or adult (e.g.~Benders, 2013). As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired and applied to lexical representations. The time is thus ripe to aggregate all publicly available evidence using a meta-analysis. In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see Frank, Braginsky, Yurovsky, and Marchman (2017); ManyBabiesConsortium (2020); for notable exceptions). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

@@

An \emph{increase} in mispronunciation sensitivity is predicted by a maturation from holistic to more detailed phono-lexical representations and has been supported by several studies (Altvater-Mackensen, 2010; Altvater-Mackensen, Feest, \& Fikkert, 2014; Feest \& Fikkert, 2015; Mani \& Plunkett, 2007). More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop. The first words that infants learn are often not similar sounding (e.g.~mama, ball, kitty; Charles-Luce \& Luce, 1995) and encoding representations for these words using fine phonological detail may not be necessary. According to PRIMIR (Curtin, Byers-Heinlein, \& Werker, 2011; Curtin \& Werker, 2007; Werker \& Curtin, 2005) infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task. A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations (Barton, Miller, \& Macken, 1980). This argument is supported by the results of Mani and Plunkett (2010). Here, 12-month-old infants were divided into low and high vocabulary groups. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations (see below for further discussion on consonant-vowel assymmetry). If increasing age and/or vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship of either with mispronunciation sensitivity.

@@

There are no theoretical accounts that would predict \emph{decreased} mispronunciation sensitivity, but at least one study has found a decrease in sensitivity to small mispronunciations . Mani and Plunkett (2011) tested 18- and 24-month-olds' sensitivity to increasingly larger mispronunciations: 1- (bed-bud), 2- (foot-fit), and 3-feature phonological changes (doll-deal). Although both age groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to more subtle 1-feature mispronunciations. To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below), as Mani and Plunkett (2011) found with 24-month-olds in their study. In contrast, 18-month-olds did not show graded sensitivity, showing similar disruptions to word recognition for smaller and larger mispronunciations.

To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size. But, this may not account for all variability found in the literature. Although infant mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image. These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. We thus follow our analyses of a developmental trajectory with one of features of the task, and line out here task effects which can shed further light on early phono-lexical representations and their maturation.

@@

@@

Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults (Nazzi \& Cutler, 2018) and infants (Nazzi, Poltrock, \& Von Holzen, 2016), known as the consonant bias. A learned account predicts that a consonant bias emerges over development (Floccia, Nazzi, Luche, Poltrock, \& Goslin, 2014; Keidel, Jenison, Kluender, \& Seidenberg, 2007; Nazzi et al., 2016) and that this emergence is impacted by the language family of the infants' native language (Nazzi et al., 2016). In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- (Mani \& Plunkett, 2007, 2010) and Danish-learning infants (Højen et al., n.d.) and do not compare infants learning different native languages (for cross-linguistic evidence from word-learning see Nazzi, Floccia, Moquet, \& Butler, 2009). One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016). In the current meta-analysis, we examine infants' sensitivity to the \emph{type of mispronunciation}, whether consonant or vowel, across different ages and native language families to assess the predictions of the learned account of the consonant bias.

@@

(Insert Figure \ref{fig:PRISMA-image} about here)

\begin{figure}
\includegraphics[width=1\linewidth]{figures/Figure_1_PRISMA_MA_Mispronunciation} \caption{A PRISMA flowchart illustrating the selection procedure used to include studies in the current meta-analysis.}\label{fig:PRISMA-image}
\end{figure}

@@

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the Google Scholar search engine to search for papers citing the original Swingley and Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (\emph{n} = 32) consisted of 27 journal articles, 1 proceedings paper, 2 theses, and 2 unpublished reports. We will refer to these items collectively as papers. Table \ref{tab:SummaryTable} provides an overview of all papers included in the present meta-analysis.

(Insert Table 1 about here)

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Condition: Were words mispronounced or not;
\item
  Mean age reported per group of infants, in days;
\item
  Vocabulary size, measured by a standardized questionnaire or list;
\item
  Size of mispronunciation, measured in features changed;
\item
  Position of mispronunciation: onset, medial, offset, or mixed;
\item
  Type of mispronunciation: consonant, vowel, or both;
\item
  Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
\item
  Distractor familiarity: familiar or unfamiliar
\end{enumerate}

@@

Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper. Most papers (\emph{n} = 52 records from 13 papers) subtracted the PTL score for a pre-naming baseline phase from the PTL score for a post-naming phase and report a difference score. Other papers either compared post- and pre-naming PTL with one another (\emph{n} = 29 records from 10 papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50\% (\emph{n} = 23 records from 9 papers). For all these comparisons, positive values or values above 50\% (either as reported or after subtraction of chance level or a pre-naming baseline PTL) indicate target looks towards the target object after hearing the label, i.e.~a recognition effect. Standardized effect sizes based on mean differences, as calculated here, preserve the sign. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.

Finally, we assess the statistical power of studies included in our meta-analysis, as well as calculate the sample size required to achieve a 80\% power considering our estimate of the population effect and its variance. Failing to take effect sizes into account can lead to either underpowered research or testing too many participants. Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (Bergmann et al., 2018). At the same time, underpowered studies with significant outcomes are likely to overestimate the effect, leading to wrong estimations of the population effect when paired with publication bias (Jennions, Mù, Pierre, Curie, \& Cedex, 2002). Overpowered studies mean that participants were tested unnecessarily, which has ethical implications particularly when working with infants and other difficult to recruit and test populations.

@@

The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R (R Core Team, 2018) package metafor (Viechtbauer, 2010). To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model. Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the package meta (Schwarzer, 2007). For a subsequent investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, type of mispronunciation, phonological overlap between target and distractor labels, and distractor familiarity (more detail below).

@@

(Insert Figure \ref{fig:FunnelCombo} about here)

@@

Heterogeneity was significant for both correctly pronounced (Q(103) = 625.63, \emph{p} \textless{} .001) and mispronounced words, (Q(146) = 462.51, \emph{p} \textless{} .001), as well as mispronunciation sensitivity, which included the moderator condition (QE(249) = 1,088.14, \emph{p} \textless{} .001). This indicated that the sample contains unexplained variance leading to significant difference between studies beyond what is to be expected based on random sampling error. In our moderator analysis we investigate possible sources of this variance.

@@

(Insert Figure \ref{fig:PlotMPEffect} about here)

@@

(Insert Figure \ref{fig:Vocabdescribe1} about here)

@@

(Insert Figure \ref{fig:PlotFeatEffect} about here)

@@

(Insert Figure \ref{fig:PlotMispPosit} about here)

@@

We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to the type of mispronunciation, consonant or vowel. Furthermore, sensitivity to consonant and vowel mispronunciations is hypothesized to differ depending on the language family of the infant's native language. We therefore conducted two sets of analyses, one analyzing consonants and vowels alone and a second including langauge family (Germanic vs.~Romance) as a moderator. We did not include data for which mispronunciation type varied within experiment and was not reported separately (\emph{n} = 23). The analysis was therefore based on a subset of the overall dataset, comparing records with consonant (\emph{n} = 145) and vowel (\emph{n} = 71) mispronunciations.

@@

(Insert Figure \ref{fig:PlotMispType} about here)

@@

(Insert Figure \ref{fig:PlotCVEffectLang} about here)

@@

When age was added as a moderator, the moderator test was significant, QM(7) = 67.82, \emph{p} \textless{} .001 and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small (\(\beta\) = 0.091, SE = 0.038, 95\% CI{[}0.017, 0.166{]}, \emph{p} = 0.016. As can be seen in Figure \ref{fig:PlotDistOverlap}b, mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap.

@@

(Insert Figure \ref{fig:PlotDistOverlap} about here)

@@

We examine whether variation in the approach to data analysis may be have an influence on our conclusions regarding infants' developing mispronunciation sensitivity. To do so, we analyzed analysis choices related to timing (post-naming analysis window; offset time) and type of dependent variable in our coding of the dataset because they are consistently reported. Further, since we observe variation in both aspects of data analysis, summarizing typical choices and their impact might be useful for experiment design in the future and might help establish field standards. In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have on reported mispronunciation sensitivity and its development. We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as a moderator.

@@

@@

Considering that we found a significant relationship between the post-naming analysis window length and infant age, such that younger ages had a longer window of analysis, we next examined whether post-naming analysis window length modulated the estimated size of mispronunciation sensitivity as infant age changed. When age was included as a moderator, the moderator test was significant (QM(7) = 247.322, \emph{p} \textless{} .001). The estimate for the three-way-interaction between condition, post-naming analysis window, and age was small, but significant (\(\beta\) = -0.04, SE = 0.014, 95\% CI{[}-0.068, -0.012{]}, \emph{p} = 0.006). As can be seen in Figure \ref{fig:PlotPostNameCondAge}b, when records were analyzed with a post-naming analysis window of 2000 ms or less (a limit we imposed for visualization purposes), mispronunciation sensitivity seems to increase with infant age. If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation between mispronunciation sensitivity and age. In other words, all three possible developmental trajectories might be supported depending on analysis choices made regarding post-naming analysis window length. These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming analysis window.

(Insert Figure \ref{fig:PlotPostNameCondAge} about here)

@@

Similar to post-naming analysis window length, all three possible developmental trajectories might be supported depending on the dependent variable reported. In other words, choice of dependent variable may influence the conclusion drawn regarding how mispronunciation sensitivity may change with infant age. We address this issue in the General Discussion.

(Insert Figure \ref{fig:PlotWithinCondAgeDiffScore} about here)
